\documentclass[12pt, letterpaper]{article}
\usepackage{SyllabusStyle}

\begin{document}
\begin{center}
	{\Large \textsc{Physical Chemistry Lab I}}

	CHEM 3615
\end{center}

\begin{center}
	{\large Fall 2024}
\end{center}
\begin{center}
	\rule{0.99\textwidth}{0.4pt}
	\begin{tabular}{llcll}
		\textbf{Instructor:} & Matthew Rowley           &  & \textbf{Office Hours:} & Daily 10:00 am -- 11:00 am \\
		\textbf{Telephone:}  & (435) 586-7875           &  &                        &  \\
		\textbf{Email:}      & matthewrowley$1$@suu.edu &  & \textbf{Office:}       & SC-220                   \\
		\multicolumn{5}{c}{Please include the course number in the subject line of all correspondence.}
	\end{tabular}
	\rule{0.99\textwidth}{0.4pt}
\end{center}

\section*{Tentative Schedule}
This class will meet on Tuesdays from 4:00pm -- 6:50pm in room 224 of the Science Center (SC)

\noindent
$\star$ Remember the literature report assignment which you should work on \emph{throughout} the semester!

\paragraph{Week 1: Aug. 28 -- Aug. 30}~

No Lab

\paragraph{Week 2: Sep. 2 -- Sep. 6}~

\begin{itemize}
  \item Group 1: Adiabatic Expansion of Gases
  \item Group 2: Measurement of the 2nd Virial Coefficient
  \item Group 3: Determination of the Caloric Content of Food
\end{itemize}

\paragraph{Week 3: Sep. 9 -- Sep. 13}~

Continue labs and work on lab reports

\paragraph{Week 4: Sep. 16 -- Sep. 20}~

\begin{itemize}
  \item Group 1: Determination of the Caloric Content of Food
  \item Group 2: Adiabatic Expansion of Gases
  \item Group 3: Measurement of the 2nd Virial Coefficient
\end{itemize}

\paragraph{Week 5: Sep. 23 -- Sep. 27}~

Continue labs and work on lab reports

\paragraph{Week 6: Sep. 30 -- Oct. 4}~

\begin{itemize}
  \item Group 1: Measurement of the 2nd Virial Coefficient
  \item Group 2: Determination of the Caloric Content of Food
  \item Group 3: Adiabatic Expansion of Gases
\end{itemize}

\paragraph{Week 7: Oct. 7 -- Oct. 11}~

Continue labs and work on lab reports

\paragraph{Week 8: Oct. 14 -- Oct. 18}~

\textbf{No Classes this week (Fall Break!)}

\paragraph{Week 9: Oct. 21 -- Oct. 25}~

\begin{itemize}
  \item Group 1: Measurement of Joule-Thompson Coefficients
  \item Group 2: Computational Study on the Enthalpy of Formation
  \item Group 3: Kinetics of the Iodination of Acetone
\end{itemize}

\paragraph{Week 10: Oct. 28 -- Nov. 1}~

Continue labs and work on lab reports

\paragraph{Week 11: Nov. 4 -- Nov. 8}~

\begin{itemize}
  \item Group 1: Kinetics of the Iodination of Acetone
  \item Group 2: Measurement of Joule-Thompson Coefficients
  \item Group 3: Computational Study on the Enthalpy of Formation
\end{itemize}

\paragraph{Week 12: Nov. 11 -- Nov. 15}~

Continue labs and work on lab reports

\paragraph{Week 13: Nov. 18 -- Nov. 22}~

\begin{itemize}
  \item Group 1: Computational Study on the Enthalpy of Formation
  \item Group 2: Kinetics of the Iodination of Acetone
  \item Group 3: Measurement of Joule-Thompson Coefficients
\end{itemize}

\paragraph{Week 14: Nov. 25 -- Nov. 29}~

\textbf{No Classes this week (Thanksgiving Break!)}


\paragraph{Week 15: Dec. 2 -- Dec. 6}~

\textbf{Final Exam}

\paragraph{Finals Week}~

No Final -- You took it last week!
\end{document}
